%=========================================================================
% sec-full-sys-physical
%=========================================================================

\section{Full-System Physical Verification Strategy}

The final phase of our overall verification strategy involves physical
verification of each ``tape-in'' produced through the previous phase. We
can divide this phase into three sub-phases: front-end verification,
back-end verification, and manufacturing verification.

\smallskip
\paragraph{Front-End Verification}
We are using Synopsys Design Compiler to synthesize the tape-in RTL into
a gate-level netlist. Front-end verification occurs on this
post-synthesis gate-level netlist.

\smallskip
\begin{cbxlist}{1.5em}{0em}{0.5em}

  \item \IT{Functional Gate-Level Simulation:} We first run the
     full-system functional tests (using the end-to-end testing framework
     described in the previous section) on the post-synthesis gate-level
     netlist without any timing information. This kind of testing can
     identify simulation/synthesis mismatch errors, tool configuration
     errors, and errors in the tools themselves.

  \item \IT{Back-Annotated Gate-Level Simulation:} We then run the
     full-system functional tests (again using the end-to-end testing
     framework described in the previous section) on the post-synthesis
     gate-level netlist with back-annotated timing information. These
     netlists may include gate-level models of mixed-signal subsystems
     (e.g., the PLL in a reduced mode of operation). This kind of testing
     can identify setup time and hold time violations, and can also
     partially verify correct integration of the processor/accelerator
     subsystems with the mixed-signal subsystems.

  \item \IT{Logical Equivalence Checking:} We use Cadence Conformal to
     perform formal equivalence checking between the original RTL and the
     post-synthesis gate-level netlist. This kind of testing can identify
     tool configuration errors and errors in the tools themselves.

\end{cbxlist}

\smallskip
\paragraph{Back-End Verification}
We are using Cadence Innovus to place-and-route the post-synthesis
gate-level netlist. We also use Cadence Innovus for floor planning, power
routing, clock routing, and I/O pad placement. The output of this
subphase is the final GDS.

\smallskip
\begin{cbxlist}{1.5em}{0em}{0.5em}

  \item \IT{Functional Gate-Level Simulation:} We run the full-system
     functional tests (using the end-to-end testing framework described
     in the previous section) on the post-pnr gate-level netlist without
     any timing information. These netlists will include the clock tree
     network along with results of gate resizing, additional buffer
     insertion, and local re-synthesis. This kind of testing can identify
     tool configuration errors, and errors in the tool themselves.

  \item \IT{Back-Annotated Gate-Level Simulation:} We then run the
     full-system functional tests (using the end-to-end testing framework
     described in the previous section) on the post-pnr gate-level
     netlist with back-annotated timing information. This kind of testing
     can identify setup time and hold time violations, and can also
     partially verify correct integration of the processor/accelerator
     subsystems with the mixed-signal subsystems.

  \item \IT{Logical Equivalence Checking:} We use Cadence Conformal to
     perform formal equivalence checking between the post-synthesis
     gate-level netlist and the post-pnr gate-level netlist. This kind of
     testing can identify tool configuration errors and errors in the
     tools themselves.

  \item \IT{Interconnect Design Rule Check:} We use Cadence Innovus to do
     a preliminary DRC check on the metal interconnect to indicate if any
     metal layer DRC rules are violated. This step helps identify
     problems before exporting and running the design through full DRC.

  \item \IT{Connectivity Check:} We use Cadence Innovus to do a
     connectivity check on the final design. This kind of check can
     detect opens, unconnected wires (geometric antennas), unconnected
     pins, loops, partial routing, and unrouted nets.

  \item \IT{Antenna Check:} We use Cadence Innovus to identify process
     antenna effects (PAE) and maximum floating area violations.

  \item \IT{Timing Check:} We use Cadence Innovus to do preliminary
     static timing analysis based on Innovus RC extraction.

  \item \IT{Block-Level Design Rule Check:} We use Calibre to do a
     block-level DRC against the foundry-provided design rules.

\end{cbxlist}

\smallskip
\paragraph{Manufacturing Verification}
We perform final verification on the GDS produced from the previous
subphase. Once these final verification steps are complete, the GDS is
ready for fabrication.

\smallskip
\begin{cbxlist}{1.5em}{0em}{0.5em}

  \item \IT{Dummy Pre-Checker Design Rule Check:} We use utilities from
     TSMC to insert extra metals and other layers to ensure density and
     manufacturability rules are satisfied. It is also required to pass
     full DRC. TSMC strongly recommends running a subset of the full DRC
     before running the Dummy Fill utilities. This identifies potentially
     unfriendly layouts in order to ensure that the geometries generated
     by utilities are legal.

  \item \IT{Full-Chip Design Rule Check:} is performed using Calibre. It
     checks the design against the foundry-provided (TSMC) design rules,
     which ensure proper manufacturing and yield. In addition to the
     standard DRC rule deck, we also run DRCs on the followi DRC antenna
     rule deck DRC bump rule deck

  \item \IT{Layout vs. Schematic Check:} compares the post-layout netlist
     versus the netlist extracted from the actual layout. This step is to
     ensure that the design was laid out correctly and matches the
     intended design.

  \item \IT{Timing Signoff:} is performed using Primetime. It uses the
     extracted parasitics from the layout to perform a timing check. This
     step ensures that the setup times and hold times for the design are
     being met. It also verifies the skew on the clock nets and reports
     clock timing. The timing checks also consider crosstalk noise on the
     nets providing a stricter timing constraint.

  \item \IT{Signal Integrity Signoff:} is performed using Primetime. It
     uses the extracted parasitics from the layout to measure
     cross-capacitance from nearby wires and check for instances where
     signals could interfere with each other. This check helps prevent
     transient errors due to signals switching at the same time. We check
     for different kinds of noise; above-low, above-high, below-low and
     below-high.

  \item \IT{IR Drop Signoff:} is performed using Cadence Voltus. It performs
     static power analysis and static and dynamic rail analysis. It
     provides the detailed leakage, internal and switching power reports
     of the design. It also analyzes the power distribution grid and
     determines voltage losses due to the resistances in the power grid
     for both the static and dynamic operations. It determines whether
     the power grid density needs to be increased to decrease the overall
     resistance to acceptable levels, otherwise transient runtime errors
     can be caused by low voltages.

  \item \IT{Electromigration Signoff:} is performed using Cadence Voltus.
     It ensures higher yields and longevity of the chip by calculating
     losses in wire integrity due to electromigration effects. This step
     is more important for high-volume, commercial products that require
     high durability.

  \item \IT{Layout Patterning Check and Shape Simulation:} is strongly
     recommended by TSMC for manufacturing. It provides the layout
     simulation according to the photo process sensitivity (photo energy,
     depth of focus, and mask error factor), after the OPC (Optical
     Proximity Correction) is applied. The purpose of LPC is to provide a
     simulation result, which we can use to avoid unfriendly designs and
     hot-spots for manufacturing. It can be run on the cell or chip
     level.

  \item \IT{Virtual Chemical Mechanical Polishing, Thickness Simulation}
     is strongly recommended by TSMC for manufacturing. It is to predict
     the thickness of the Cu \& IMD across the die and to identify the
     critical non-uniform metal thickness as hot-spots. It allows us to
     minimize the thickness variation by proper dummy filling or metal
     slotting.

\end{cbxlist}
