%=========================================================================
% sec-intro
%=========================================================================

\section{Introduction}

This document describes the verification strategy being used for the
current CERTUS SoC tapeout on the next CRAFT MPW run.  Our verification strategy is designed to evolve in step with the advances in synthesis and composition methods being pursued in the project. Accordingly, our verification methodology builds upon existing tools and tool flows with parts that are subject to improvement using iterative refinement of the design flow. This document uses commonly accepted terminology where `testing' refers to methods that validate a design against a given testbench via methods that ultimately result in a simulation run followed by comparison of results against an explicit or implicit golden reference. Verification on the other hand usually refers to methods that seek to establish confidence in the design independent of the simulation conditions either exhaustively or through implicitly exhaustive (such as formal) methods. Term 'validation' is sometimes used to refer to both strategies collectively even though it is also used interchangeably with ``verification.'' This document does not concern with the issue of manufacturing test where standard circuit level testing methodology is deployed across the entire chip design.

%This strategy is a
%work-in-progress and is continuing to evolve as we make progress towards
%the final tapeout deadline. 
%This document also includes discussion of our
%future plans for improving this verification strategy in the later phases
%of the program.

\input{fig-toplevel-block-diagram}

Figure~\ref{fig-toplevel-block-diagram} illustrates the top-level block
diagram for the first CERTUS SoC tapeout which includes three key
components: the processor subsystem, accelerator subsystem, and the
mixed-signal subsystem. The \IT{processor subsystem} includes a set of
four RISC-V RV64G Rocket cores each with their own instruction and data
caches. The Rocket cores control a large array of small RISC-V RV32IM
Vanilla-5 cores through the rocket custom coprocessor (RoCC) interface.
Each Vanilla-5 core has its own small instruction and data memory, and
these cores are interconnected through a mesh on-chip network. The cores
communicate to the rest of the chip through the \TT{bsg\_tag} interface
for configuration and through NASTI interfaces (similar to AXI) for
memory management. A smaller ten-core Vanilla-5 array is also included as
a separate part of the processor subsystem; this array serves as a test
vehicle for the digital low-drop-out regulator. The \IT{accelerator
  subsystem} includes a RISC-V RV64G Rocket core which controls a
binarized neural network (BNN) accelerator through the RoCC interface.
Again, the Rocket core communicates to the rest of the chip through the
\TT{bsg\_tag} interface for configuration and through a NASTI interface
for memory management. The \IT{mixed-signal subsystem} includes a
synthesizable phase-locked loop (PLL) to generate various on-chip clock
signals for the entire chip, along with a synthesizable digital
low-drop-out (DLDO) regulator. The PLL and DLDO subsystems are configured
through dedicated off-chip interfaces (either SPI or direct input pins).
These three subsystems are integrated into a full-system via the
\IT{basejump I/O} which includes adapters to convert NASTI interfaces
into a simpler internal message interface and then a centralized bus to
enable the various subsystems to communicate off-chip. Off-chip
communication is via a simple multi-channel source-synchronous protocol
called \TT{bsg\_comm\_link}.

\input{fig-verification-flow}

Figure~\ref{fig-verification-flow} illustrates the five parts 
of our overall verification strategy. Our SOC design proceeds bottom with the design (or import) of each of the three subsystems mentioned earlier. Thus, each subsystem is first tested in isolation during its design phase before it is composed into full chip design and then subject to full-chip functional and physical verification. Note that the tight-coupling of processor and accelerator subsystems requires their integration and validation. The CERTUS team has devised a processor and accelerator core interface to not only enable robust composition of these two subsystems as well has simplify the validation process as well that is discussed in the following section.

In the following we list the steps taken in each of the five parts followed by a description of rationale and tools used. This is followed by a detailed description of the verification methodology pursued in accelerator design, the primary target of CERTUS architectural and methodological improvements.

\medskip
\begin{cbxlist}{1.5em}{1em}{1em}

 \item The \IT{processor subsystem functional RTL verification strategy}
    is centered around functional testing via executable descriptions of the processor subsystem. Given a well-defined operational semantics of the processor functions, {\bf model execution} provides the easiest and fastest means to validate this system. Most modern validation tools provide the capability to automatically generate randomized testbenches under user-specified constraints for processor-centric designs. Using these facilities, we perform the following individual tests of main components:

    \smallskip
    \begin{cbxlist}[--]{1.5em}{0em}{0em}
      \raggedright

      \item test BSG RTL component library using directed and random
         unit tests;
      \item test the on-chip network RTL using directed and random
         tests;

      \item test single Vanilla-5 core RTL using self-checking
         assembly test programs;

      \item test the Vanilla-5 ten-core/manycore RTL using small C
         test programs;

      \item test a single Rocket core RTL using self-checking
         assembly and small C test programs;

      \item test of the Rocket+manycore RTL using small C test programs.

    \end{cbxlist}

 \item The \IT{accelerator subsystem functional RTL verification
   strategy} consists of a combination of algorithm validation, testing of the accelerator and processor composition and validation of the accelerator design as it goes through iterative refinement and high-level synthesis processes. The latter are subject to new methodological improvements discussed later in this report. In particular, we performn the following steps:

    \smallskip
    \begin{cbxlist}[--]{1.5em}{0em}{0em}
      \raggedright

      \item validation of algorithm using a high-level description of the
         algorithm to be accelerated;

      \item testing the manually written C++/SystemC implementations of
         the algorithm using the \\\hspace{0.5em}high-level description
         of algorithm as a golden reference;

      \item testing the RTL generated automatically through high-level
         synthesis (HLS) using the \\\hspace{0.5em}C++/SystemC
         implementations as a golden reference;

      \item testing the Rocket+accelerator RTL using self-checking
         assembly and small C test programs;

      \item testing complete end-to-end workload scenarios.

    \end{cbxlist}

 \item The \IT{mixed-signal subsystem functional verification} uses a combination of digital circuit validation as well as post-silicon validation. {\bf The latter forms a major component of our innovations and attempts to improve the SOC design and validation process that seeks to dramatically reduce the time used in pre-silicon design and validation tasks.} In particular, of mixed-signal validation strategy consists of the following steps that are designed to run in parallel for different analog blocks:

    \smallskip
    \begin{cbxlist}[--]{1.5em}{0em}{0em}
      \raggedright

      \item validating the PLL functional design using a system-level model;

      \item testing the PLL RTL and gate-level models using system-level
         model results as a golden reference;

      \item testing the PLL extracted transistor-level models using
         system-level model simulation results as a golden reference;

      \item testing the DLDO custom cell transistor-level models using
         {\bf directed unit tests};

      \item testing the DLDO RTL and gate-level models using directed
         unit tests;

      \item using DLDO {\bf post-silicon configuration} to avoid pre-silicon
         verification.

    \end{cbxlist}

 \item The \IT{full-system functional verification strategy} is 
 built around the concepts of progressively complex ``tape-ins'' towards a final ``tape-out''. This structure obviates the need for commonly used 
 `regression runs' early in the chip design process and reduces the amount of validation task significantly at the full-chip level. In the CERTUS context, each tape-in is an instance of a complete chip, but which only
    implements a subset of the desired final functionality. Tape-ins are
    taken through both functional and physical verification. Each tape-in
    gradually adds more complexity until we converge on the final
    full-system. Each tape-in includes the basejump I/O for communicating
    with the final test board including the \TT{bsg\_comm\_link} and
    \TT{bsg\_tag} interfaces and the actual gateware that will be present
    in the test board's FPGA. Tape-in functional verification is done
    primarily through RTL simulation using either directed tests or
    assembly/C test programs. The set of incremental tape-ins are:

    \smallskip
    \begin{cbxlist}[--]{1.5em}{0em}{0em}
      \raggedright

      \item basejump I/O;
      \item basejump I/O with single Vanilla-5 core;
      \item basejump I/O with Vanilla-5 ten-core;
      \item basejump I/O with single Rocket core;
      \item basejump I/O with Rocket+manycore composition;
      \item basejump I/O with Rocket+accelerator composition;
      \item basejump I/O with Rocket+manycore and Rocket+accelerator composition;
      \item basejump I/O with single Rocket core with the PLL;
      \item basejump I/O with Vanilla-5 ten-core with the DLDO;
      \item basejump I/O with Rocket+manycore, Rocket+accelerator,
         Vanilla-5 ten-core, PLL, DLDO.

    \end{cbxlist}

 \item The \IT{full-system physical verification strategy} takes each
    tape-in through all of the front-end, back-end, and manufacturing
    verification steps including:

    \smallskip
    \begin{cbxlist}[--]{1.5em}{0em}{0em}
      \raggedright

      \item post-synthesis functional gate-level simulation;
      \item post-synthesis back-annotated gate-level simulation;
      \item post-synthesis logical equivalence checking against RTL;
      \item post-pnr functional gate-level simulation;
      \item post-pnr back-annotated gate-level simulation;
      \item post-pnr logical equivalence checking against post-synthesis
         gate-level netlist;
      \item post-pnr connectivity, antenna, timing check;
      \item post-pnr block-level design rule check;
      \item full-chip design rule check;
      \item full-chip layout vs schematic check;
      \item full-chip timing signoff;
      \item full-chip signal integrity signoff;
      \item full-chip IR drop signoff;
      \item full-chip electromigration signoff;
      \item full-chip layout patterning check and shape simulation;
      \item full-chip virtual chemical mechanical polishing check and
         thickness simulation.

    \end{cbxlist}

\end{cbxlist}

\medskip\noindent
In the rest of this document, we detail each of the
five phases of our overall verification strategy. We also describe our
use of preliminary tape-outs to help verify subsystems, and future plans
for improving this verification strategy as part of phase 2 and 3 of the
program.
