%=========================================================================
% sec-full-sys-functional
%=========================================================================

\section{Full-System Functional Verification Strategy}

Each tape-in is an instance of a complete chip, but which only implements
a subset of the desired final functionality. Each tape-in gradually adds
more complexity until we converge on the final full-system. Each tape-in
includes the basejump I/O and adheres to the pin-out constraints of the
final chip. Each tape-in supports end-to-end testing in simulation of the
BaseJump Daughterboard from the gateway FPGA firmware out to the PCB and
into the ASIC. Each tape-in comes with tests that are loaded into the
gateway FPGA, which then drive packets through the \TT{bsg\_comm}
interface to accurately simulate communication between the gateway FPGA
and ASIC. The exact same testing infrastructure can be used to test an
actual tape-out, and indeed this is a key part of our post-silicon
bring-up strategy for the final CERTUS SoC. Each of the incremental
tape-ins are briefly described below.

\smallskip
\begin{cbxlist}{1.5em}{0em}{0.5em}
  \raggedright

  \item \IT{Basejump I/O:} Our first tape-in includes just the basejump
     I/O for loop-back testing. This tape-in helps test the
     source-synchronous off-chip communication interfaces, the on-chip
     asynchronous interfaces, and the overall end-to-end testing
     methodology. This tape-in also enables testing the \TT{bsg\_tag}
     interface: a write-only JTAG-like interface that uses 3 pins to set
     configuration bits on multiple devices in a chain. Later physical
     verification of this tape-in enables testing pad-ring instantiation
     in our ASIC flow.

  \item \IT{Basejump I/O with Single Vanilla-5 Core:} This tape-in
     includes a single Vanilla-5 core along with the associated SRAMs for
     instruction and data memories. Self-checking test programs are
     loaded from the gateway FPGA into the Vanilla-5 cores' instruction
     memory through the basejump I/O and \TT{bsg\_comm} interface. The
     Vanilla-5 core can send test results back to the gateway FPGA also
     through the basejump I/O and the \TT{bsg\_comm} interface. Later
     physical verification of this tape-in enables testing the use of
     SRAMs in our ASIC flow.

  \item \IT{Basejump I/O with Vanilla-5 Ten-Core:} This tape-in includes
     ten Vanilla-5 cores interconnected through a simple mesh network.
     The mesh network is directly connected to the basejump I/O and
     \TT{bsg\_comm} interface. This enables the gateway FPGA to send and
     receive messages through the on-chip mesh network. As with the
     previous tape-in, self-checking test programs can be loaded from the
     gateway FPGA into each of the Vanilla-5 cores' instruction memories,
     and the Vanilla-5 cores's can send test results back to the gateway
     FPGA. Later physical verification of this tape-in enables testing
     the hierarchical ASIC flow.

  \item \IT{Basejump I/O with Single Rocket Core:} This tape-in includes
     a single rocket core with nothing attached to the RoCC interface.
     The back-side of the Rocket instruction and data caches use the
     NASTI interface from UC Berkeley. Adapters are used to connect this
     interface to the basejump I/O. Memory requests due to cache misses
     from the Rocket core are serviced by the gateway FPGA through the
     \TT{bsg\_comm} interface. A self-checking test program is loaded
     into the gateway FPGA and executed by the Rocket core after reset.
     The gateway FPGA can snoop memory write requests from the Rocket
     core to check the test results.

  \item \IT{Basejump I/O with Rocket+Manycore Composition:} This tape-in
     includes the single Rocket core from a previous tape-in composed
     with the Vanilla-5 manycore. The Rocket core manages the Vanilla-5
     manycore via the RoCC interface. As in the previous tape-in the
     back-side of the Rocket instruction and data caches are connected to
     the basejump I/O and gateway FPGA. The Vanilla-5 manycore does not
     have a direct connection to the basejump I/O. A self-checking test
     program is loaded into the gateway FPGA and executed by the Rocket
     core after reset. This test program will in turn load instructions
     and data into the Vanilla-5 manycore. The Rocket core will monitor
     the execution of the Vanilla-5 manycore and write results to main
     memory. The gateway FPGA can snoop memory write requests from the
     Rocket core to check the test results.

  \item \IT{Basejump I/O with Rocket+Accelerator Composition:} This
     tape-in includes the single Rocket core from a previous tape-in
     composed with the BNN accelerator. The Rocket core manages the BNN
     accelerator via the RoCC interface. As in the previous tape-in the
     back-side of the Rocket instruction and data caches are connected to
     the basejump I/O and gateway FPGA. A self-checking test program is
     loaded into the gateway FPGA and executed by the Rocket core after
     reset. This test program will in turn configure and start the BNN
     accelerator. Note that unlike the Rocket+Manycore composition, the
     BNN accelerator has a direct connection to the Rocket data cache and
     will cause its own memory requests to go out to the gateway FPGA.
     The Rocket core will monitor the execution of the BNN accelerator,
     and ensure all test results are flushed to the gateway FPGA for
     verification.

  \item \IT{Basejump I/O with Rocket+Manycore and Rocket+Accelerator
    Composition:} This tape-in simply composes the previous two tape-ins.
     Testing is identical to the approach used in the previous tape-ins.
     This tape-in helps test the ability of the basejump I/O to support
     multiple clients and for the gateway FPGA to manage multiple memory
     request streams from different on-chip Rocket cores.

  \item \IT{Basejump I/O with Single Rocket Core with the PLL:} This
     tape-in includes the single Rocket core from a previous tape-in with
     the on-chip synthesizable PLL. The PLL is configured through a
     dedicated off-chip SPI interface and generates the clock for the
     Rocket core. Co-simulation of the Rocket RTL and PLL gate-level
     models is possible through careful configuration of the PLL to avoid
     the need for behavior which cannot be captured in gate-level
     simulation. Later physical verification of this tape-in enables
     testing integrating mixed-signal clocking subsystems into our ASIC
     flow.

  \item \IT{Basejump I/O with Vanilla-5 Ten-Core with the DLDO:} This
     tape-in includes the Vanilla-5 ten-core from a previous tape-in with
     the on-chip synthesizable DLDO. The DLDO does not really play a role
     in RTL verification, so the primary purpose of this tape-in is to
     enable later physical verification of integrating mixed-signal power
     regulation subsystems into our ASIC flow.

  \item \IT{Basejump I/O with Rocket+Manycore, Rocket+Accelerator,
    Vanilla-5 Ten-Core, PLL, DLDO:} This is the final tape-out which
     composes the previous tape-ins into the complete CERTUS SoC. The
     Rocket+manycore, Rocket+accelerator, and the Vanilla-5 ten-core are
     connected to the basejump I/O and then the \TT{bsg\_comm} interface;
     the mixed-signal DLDO is connected to the top-level configuration
     pins and the Vanilla-5 ten-core; and the mixed-signal PLL is
     connected to its dedicated off-chip SPI interface and is used to
     clock the entire chip. The \TT{bsg\_tag} interface is used where
     necessary for out-of-band configuration. For example, the
     \TT{bsg\_tag} interface can disable a subsystem (e.g., one of the
     Rocket cores) or enable scanning out specific internal buses for
     post-silicon debugging and testing.

\end{cbxlist}

